Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/introduction.tex
typo fix

Verification tools for network configurations~\cite{batfish} have been developed as a complimentary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent. However, existing verification tools have their drawbacks: like templates, they do not help operators come up with the configuration in the first place, and moreover, they can only check correctness under concrete environment and failure scenarios, rather than under all possible environments and failure scenarios.

>>>>

Verification tools for network configurations~\cite{batfish} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent. However, existing verification tools have their drawbacks: like templates, they do not help operators come up with the configuration in the first place, and moreover, they can only check correctness under concrete environment and failure scenarios, rather than under all possible environments and failure scenarios.
